Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-12 Grassmannian_cells.tex
nearly finished section 5
last bit of main theorem and proof-reading are missing

\newtheorem{theorem}{Theorem}[section]
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
\noindent 
We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_m)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.  For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}\label{recursive}\tilde P_m=(\tilde\Sigma_1 \tilde P_{m-1})^T,\quad\tilde P_{m+1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\footnote{odd and even live on different components}\end{align}
Recall that we obtain the Auslander-Reiten translate $\tau^{-1}\tilde P_m$ by applying the reflection functor to the sinks twice where the sinks become sources after each step. 
\begin{remark}\begin{enumerate}
\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,0)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
\end{enumerate}
\end{remark}
The next step is to construct filtrations of $\tilde P_m$ by smaller preprojective $w.\tilde P_{l}$ for $l<m$ and certain $w\in W_Q$. To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. More precisely, we have 
$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l+1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}). In the following, we sometimes identify the arrows with the numbers $1,\ldots,n$.

We need some more notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$

Let
$$I^n_l:=\{(i_1,\ldots,i_{l})\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows. For $\ui=(i_1,\ldots,i_{n-1})\in I_{n-1}$, let $i^c\in \{1,\ldots,n\}$ and $\ui^c=(i^c)$ where $i^c\neq i_j$ for $j=1,\ldots,n-1$. Clearly, $\ui^c$ is uniquely determined by $\ui$.

Let $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ be a sequence with $\underline{i_1}\in I_{n-1}$, $\underline{i_2},\ldots,\underline{i_{r-1}}\in I_{n-2}$ and $\underline{i_r}\in I_s$ for $s\leq n-2$. Define $i_1^c$ as before and for $k\geq 2$ let $i_k^c\in\{1,\ldots,n\}$ be the unique number such that $i_k^c\neq i_{k,j}$ for $j=1,\ldots,n-2$ and $i_k^c\neq i_{k-1}^c$. We say that $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ is admissible if 
$$ i_{k,j}\neq i_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,j=1,\ldots,n-2\text{ and for }j=1,\ldots,s\text{ if }k=r.$$

For $\ui\in I_{s}$ with $s\leq n-1$, there exist unique exact sequences of the form
\[\ses{\bigoplus_{j=1}^s\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{\ui}},\quad\quad\ses{\tilde P_{m-1,i_s}}{\tilde P_{m}^{(i_1,\ldots,i_{s-1})}}{\tilde P_{m}^{\ui}}\]
where the $\tilde P_m^{\ui}$ are truncated preprojectives (as defined in the last section). The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf i}=(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$. We define the admissible sequence $\delta {\bf i}$ (of length $r-1$) by
\[\delta {\bf i}:=((i_1^c,\underline{i_2}),\ldots,\underline{i_r}).\]
We recursively define $\delta^l{\bf i}$ for $l=1,\dots,r-1$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\ui=(i^c)$ for $\ui\in I_{n-1}$.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{j=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The representations $\tilde P_{m,j}$ are pairwise orthogonal, i.e. for $j\neq i$ we have $$\Hom(\tilde P_{m-1,i},\tilde P_{m-1,j})=\Ext(\tilde P_{m-1,i},\tilde P_{m-1,j})=0;$$
    \item If $\ui\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\ui}\cong \tilde P_{m-1,i^c}^{\ui^c}= P_{m-1,i^c}/P_{m-2,(i^c,i^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf i:=(\underline{i_1},\ldots,\underline{i_r})$ be an admissible sequence. Let ${\bf i}(l):=(\underline{i_1},\ldots,\underline{i_l})$ for $l=2,\ldots,r-1$. Then we recursively have
		\[\tilde P_{m-l,(i_1^c,\ldots,i_l^c)}^{\delta^l{\bf i(l)}}=\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}\bf i(l)}\]
		for $l=1,\ldots,r$. Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf i}_{m-r+1}:=\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}/\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{(i_{r-1}^c,i_{r,1},\ldots,i_{r,s})}$$ with each admissible sequence ${\bf i}$.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows from Theorem \ref{covering}. For $m=2$, the second part is obvious. For $m\geq 3$, it then follows by applying the identities (\ref{recursive}).

To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-1}\tilde P_{m-1,i_j}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\ui}\ar[r] & 0 \\
  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,i^c}\ar[u]\ar[r]& \tilde P_{m}^{\ui}\ar[r]\ar@{=}[u]& 0}\]

%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,i^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(i^c,i^c)}$. Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,i^c}^{\ui^c}$. Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.

The forth statement is now obtained recursively when initially considering the diagram from above replacing $\ui$ by $\underline{i_1}$.

We have $\delta^{l-1}{\bf i}(l)=(i_{l-1}^c,i_{l,1},\ldots,i_{l,n-1})$. We use the third statement in order to successively obtain commutative diagrams
\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-2}\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})}\ar[r] &  \tilde P^{(i_{l-1}^c)}_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}\ar[r] & \tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}{\bf i}(l)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-(l+1),(i_1^c,\ldots,i_{l}^c,i_l^c)} \ar[r]\ar[u] & \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}\ar[u]\ar[r]& \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}^{(\underline{i_{l}^c)}}\ar[r]\ar@{=}[u]& 0}\]
Now we have $\delta^l{\bf i}(l)=(i_l^c)$.	Finally, we consider the short exact sequence:

\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{s}\tilde P_{m-r,(i_1^c,\ldots,i_{r-1}^c,i_{r,j})}\ar[r] &  \tilde P^{(i_{r-1}^c)}_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{{\bf i}}\ar[r] & 0 }.\]
As $\Hom(\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})},\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)})=k$ for all $l=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf i}$ is uniquely determined.
	\end{proof}
We denote the quotient morphism by $\pi_m^{\bf i}:\tilde P_m\to \tilde P_{m-r+1}^{\bf i}$. It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{(1,\ldots,l)}$ where $l\leq n-1$ and $j_k\neq i_1^c$ for $k=1,\ldots, l$. We also denote the quotient morphism from $\tilde P_m^{(j_1,\ldots,j_l)}$ to $\tilde P_{m-r+1}^{\bf i}$ by $\pi_m^{\bf i}$.

@@

\end{proof}
\begin{theorem}\label{cellscover}
Let $\uj=(i_1,\ldots,i_l)$ be an admissible sequence. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}

>>>>

\newtheorem{theorem}{Theorem}[section]
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
\noindent 
We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$. Moreover, sinks become sources and vice versa. For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\end{align}
It is rather important that $\tilde P_{2m}$ and $\tilde P_{2m-1}$ live on two different components of the universal covering quiver.

\begin{remark}\begin{enumerate}
\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
\item Then we have 
$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,1)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
\end{enumerate}
\end{remark}

%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.

\begin{example}\label{smallm}[The cases $m=2,3,4$]
\end{example}

The representation $\tilde P_2$ is given by the following coefficient quiver:

\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
The coefficient quiver of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.

Using this notation, we obtain that $\tilde P_3$ can be written as
	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
	and, moreover, $\tilde P_3^{\uj}$ is obtained when erasing the subquiver $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of the sink by one.  The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,j_l}=a_{j_l}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $\bullet\xrightarrow{a_{j_l}}\bullet$.

The support of $\tilde P_4$ is given by
\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
where the numbers correspond to the dimensions of the respective vertices. Moreover, all dimensions on the subquivers $\mathcal A_i$ are one. The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$. Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]

\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau^{-1}$ is given by reflecting at all the sinks first and at all sources afterwards. Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.

%\begin{tikzpicture}[scale=1]
%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
%\end{tikzpicture}

\begin{remark}
Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}). We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective. Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
\end{remark}

The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$

Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows. For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ and $\uj^c=(j^c)$ where $j^c\neq j_i$ for $i=1,\ldots,n-1$. Clearly, $\uj^c$ is uniquely determined by $\uj$.

\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$. Define $j_1^c$ as before.
 We say that ${\bf j}$ is admissible if 
$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
where $j_k^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique number satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
\end{definition}

For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}\]
where the $\tilde P_m^{\uj}$ are lifts of truncated preprojectives (as defined in the last section). The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$. We define the admissible sequence $\delta {\bf j}$ (of length $r-1$) by
\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\ldots,\underline{j_r}).\]
We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r-1$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. Let ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$. Then we recursively have
		\[\tilde P_{m-l,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-l+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
		for $k=1,\ldots,r$. Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$%/\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}$$ 
		with each admissible sequence ${\bf j}$.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).

To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]

%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,j^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$. Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,j^c}^{\uj^c}$. Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.

The forth statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$. We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$. We use the third statement in order to successively obtain commutative diagrams
\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
Now we have $\delta^{k-1}{\bf j}(k)=(j_k^c)$.	Finally, we consider the short exact sequence:

\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
	\end{proof}
We denote the quotient morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$. Let $\ui=(i_{1},\ldots,i_{l})$. It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{\ui}$ where $l\leq n-1$ and $i_k\neq j_1^c$ for $k=1,\ldots, l$. We denote the quotient morphism from $\tilde P_m^{\ui}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\ui}^{\bf j}$.

Our construction immediately yields the following lemma.
\begin{lemma}\label{projections}
Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$. Then we have
\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}\]
and, for any sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
for $k=1,\ldots,r-1$ where $\pi_{m,j_{-1}^c}^{\underline{j_1}}:=\pi_m^{\underline{j_1}}$ and the analogous statement for $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ and $(l_1,\ldots,l_{s-1})\in I_{s-1}$ holds.
\end{lemma}
We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$. Therefore, we need to apply a translated version of this morphism. In abuse of notation, we also denote this morphism $\pi_m^{\bf j}$.

@@

\end{proof}
\begin{theorem}\label{cellscover}
Let $m\geq 2$ and let $\uj=(j_1,\ldots,j_l)\in I_l$ with $l\leq n-1$. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
